\begin{abstract}

One of the main challenges
in designing lessons
for an introductory
information security class
is how to present new technical concepts
in a manner comprehensible to students
with widely different backgrounds.
In situations like these, a non-traditional approach
can help students
engage with the material
and, in doing so,
master
these unfamiliar ideas.
We have devised a series of lessons that teach important information security
topics, such as social engineering,
side-channel attacks,
and
attacks on randomness
using card magic.
Each lesson
centers around a card trick
that illustrates how the attack works
in a manner that incorporates
student participation.
In this work,
we describe our experience using these lessons in teaching
cybersecurity topics
to high school students with limited computer science backgrounds.
Students were assessed
before and after the demonstration
to gauge their mastery of the material,
and their
opinions on each lesson.
In addition to very positive student responses
during the lesson,
our pre- and post-tests
showed that student scores for each topic improved by between 15\% and 30\%
after attending our demonstration.
Students reported that they enjoyed the lesson,
found card magic to be a useful tool,
and felt the demonstration
improved their mastery of the material.

\end{abstract}

%Hand-waving away the technical background behind these concepts is bad...
%
%...and undermines student's motivation to learn and understand the material.
%
%Bypassing the need for technical explanation while preserving the main
%  focus of the lesson.
