\section{Study Instrument and Evaluation}
\label{SEC:evaluation}

\paragraph{Method}The goal of our study was to judge how effective a non-traditional approach
could be in teaching novices about our selected attacks.
Unfortunately, making such a judgment was hampered by
necessary accommodations
required by COVID-19 restrictions.
We adapted our lesson into
a 90 minute Zoom session and offered it as a optional class during
a remote-learning computer science summer camp for high school
students.  This not only limited interaction, but also
forced changes in how we handled the needed consent and permission forms.


We measured improvement in mastery
of the material
using
an  assessment (a portion of which is shown in Table~\ref{fig:assessment})
consisting of
12 multiple choice questions (4 for each topic),
3 Likert-scale survey statements,
and a free response comments section.
To best accommodate the student's needs we converted our
assessment to an online, rather than a paper form we could have distributed
immediately before and after the session.
The students were instead
asked to complete the assessment once before the lesson to
generate a baseline and once after the lesson to measure improvement
and gather student opinions.
Of the 15 students that attended our session, 10 agreed to participate in
the study and 5 completed it.
The fall off in study completion can be attributed to
an inability to
do the assessment in person and to
follow up about the post-test.  In spite of these
challenges, we are able to demonstrate substantial improvement in aggregate
scores across all assessed topics.



%All of these materials were reviewed and approved by our university's
%Institutional Review Board and, though attendance was open to all, we only
%used data from students who had given us their consent to be part of the
%study.


%They were asked to complete it once

%completed the 12 multiple choice questions twice,
%once before our lecture to gather a baseline of
%participants' existing knowledge of the material,
%and again at the conclusion of our
%lecture as a post-test to determine if student mastery improved.
%Both assessments used the same questions.
%The post-test was handed out at the conclusion of the lesson
%and students were asked
%to complete it in their own time.

%to be presented at a summer
%computer science workshop for high school students.  The session was
%offered twice during the three week workshop, with the lead investigator
%serving as the presenter and magician.  It was divided into three phases,
%one
%for each topic,
%and each phase consisted of a performance of the topic's magic
%trick, followed by a detailed discussion that used the magic trick
%as a scaffold.  A total of 15 students attended the two sessions.


%Given the overwhelmingly
%positive feedback we received from our session attendees, we believe the
%decreased number of participants completing the post test can likely
%be attributed
%to the awkwardness of an interactive session online
%rather than deficiencies in
%the session itself.


\begin{table}[h]
  \scriptsize
  \begin{tabular}{c | p{6cm}}
Question Text  &     \\
\hline
Q1 & Which of the following is the best definition of social engineering \\
Q2  & The act of creating a scenario in order to extract information is called:   \\
Q3 & What of the following pieces of information are dangerous to reveal online?  \\
Q4  & Bad actors can use stolen personal information to do which of the following: \\
Q5 & What is a side channel attack?  \\
Q6  & Which of the following can give you a hint as to what a computer is doing?   \\
Q7 & What is an example of a common real-world side channel attack? \\
Q8  & How could you prevent an attacker from stealing a password by using a microphone to listen to keystrokes?\\
Q9 & Which of the following is a major use of hash functions? \\
Q10 & Which of the following is an important feature of a good hash function  \\
Q11 & When passing multiple items sequentially into a hash function, which item has the most influence on the output \\
Q12 & What is the term used when two or more inputs to a hash function generate the same output? \\
%\hline
%S1 & The lesson today increase my knowledge in the areas we covered. \\
%S2  & The manner in which the material was presented helped me understand the material better\\
%S3 & I enjoyed the manner in which the material was presented  \\
\end{tabular}
\caption{Multiple choice questions used on our assessment.}
\label{fig:assessment}
\end{table}



\begin{table}
  \centering
  \scriptsize
  \begin{tabular}{c | l | l}
Question &  Correct on Pre-test   & Correct on Post-test \\
\hline
Q1   & 3 (60\%)  & 5 (100\%) \\
Q2   & 3 (60\%)  & 4 (80\%)  \\
Q3   & 5 (100\%) & 5 (100\%) \\
Q4   & 2 (40\%)  & 5 (100\%) \\
\hline
Q5   & 0 (0\%)   & 0 (0\%)   \\
Q6   & 5 (100\%) & 5 (100\%) \\
Q7   & 4 (80\%)  & 5 (100\%) \\
Q8   & 3 (60\%)  & 5 (100\%) \\
\hline
Q9   & 4 (80\%)  & 3 (60\%)  \\
Q10  & 4 (80\%)  & 4 (80\%)  \\
Q11  & 1 (20\%)  & 5 (100\%) \\
Q12  & 2 (40\%)  & 5 (100\%) \\
\end{tabular}

%\begin{tabular}{ c | l}
%Statement & Aggregate Responses \\
%\hline
%S1 &  Strongly Agree: 4 Agree: 1 \\
%S2 &  Strongly Agree: 4 Agree: 1 \\
%S3 &  Strongly Agree: 5 \\
%\end{tabular}}
\caption{Aggregate scores for each assessment question. Q1-Q4 covered
  social engineering, Q5-Q8 covered side channel attacks, and Q9-Q12
  covered attacks on randomness.}
%Rows S1, S2, and S3 report number of participants that selected the listed response.  Likert responses that were not chosen by any participant are omitted.
\label{fig:results}
\end{table}

\paragraph{Results}
Aggregate scores increased across all categories on the post-test.
The results in Table~\ref{fig:results} show scores for the social engineering and attacks on randomness sections
increased by 30\% while the side channel attacks section increased by
15\%.
The improvement in social engineering scores can be traced to
higher scores on
Q1, Q2, and Q4,
indicating a better understanding of the topic.
Smaller improvements on Q5 and Q9 suggest a need to improve the lesson in
these specific areas.  We have already made these improvements for future
sessions.
Accurate responses to Q11 and Q12
suggest the students have learned two
key properties of hash functions.
Aggregate scores increased across all categories on the post-test.


Student offered very positive opinions about the lessons.
All students
either ``strongly agreed'' or ``agreed''
that the lesson improved their skills in the covered topics
and was enjoyable.
More than half of students offered free response comments describing the
session as ``fun,'' ``entertaining,'' and ``interesting.''  One response
found the side-channel attack using upside-down cards
was particularly useful.


%Encouragingly, the students were well aware of
%what information should not be shared online suggesting they have been
%warned about these dangers in other places.
%The improvements in scores related to attacks on randomness
%came largely
%from more
%These questions are particularly important because
%correct answers
%The smallest improvement (15\%) came about in the side channel attacks
%scores.
%Small improvements on Q10 scores and no improvement on Q5 and Q9 indicate
%shortcomings in our lesson.  We have made improvements to related areas of
%the lesson for future sessions



%Comparing aggregate pre-test and post-test results show an improvement of
%AAA\%.  The majority of this improvement came from better scores on the
%hash function-related questions.  This improvement likely comes from our
%participant population's lack of experience with the area.  The details of
%hash functions are likely to be covered in undergraduate course work rather
%than high-school computer science classes.
%
%The next most-improved topic was side channel attacks.  Questions 6 and 7
%showed a marked improvement from AAA\% correct to BBB\% correct.  Answering
%these questions correctly requires students to understand the theory
%behind side
%channel attacks and apply it to several scenarios to identify the correct
%response.  As a result,  improved scores on these questions indicate deeper
%mastery of the material rather than simple memorization of a definition.
%
%The questions related to social engineering showed some improvement, though less
%than the other areas.  This is due to most participants correctly answering
%these questions on the pre-test.  It is likely students currently
%attending high school grew up in a time where education about scams and
%safety on the internet has been ongoing from an early age.


\paragraph{Instructor Observations}
The session's instructor observed that student experience during
the session was overwhelmingly positive considering
the difficulties imposed by a remote teaching modality required by COVID-19
restrictions.
In a remote setting, camera usage
and responsiveness are two key indicators of student engagement.
In both sessions a significant majority of students kept their cameras on
when participating in a trick, and asking or answering questions
about the material.
%Students remained attentive and focused throughout
% the lesson suggesting that our
%style of presentation can help maintain attention during a moderately long,
%technical lecture.
Students were also
eager to analyze the
tricks, put forward hypotheses about how they worked,
and expand on important aspects of the material.
Further, students readily volunteered to participate in spite
of the unusual teaching modality created by a remote presentation,
along with the general discomfort of being in a
prominent position ``at the front of class.''
After the session,
several
made
unprompted verbal statements about how much they enjoyed the
lesson and how the magic tricks aided their understanding of the
material.
